A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
Fix escaping

The \c{imchange} function of package \c{imager} makes it possible to modify images using a dedicated formula syntax using \c{~}.\footnote{Inspired by \c{map} in package \emph{purr}.}  Here, \eval is evaluated in \c{newenv}, which creates a new environment that inherits from \c{parent.frame()} by default. We classify it as 1+.

>>>>

The \c{imchange} function of package \c{imager} makes it possible to modify images using a dedicated formula syntax using \c{\~}.\footnote{Inspired by \c{map} in package \emph{purr}.}
Here, \eval is evaluated in \c{newenv}, which creates a new environment that inherits from \c{parent.frame()} by default. We classify it as 1+.
